\section{Section}

\subsection{Subsection}

This template is used to prepare manuscripts for works in cryptography.%
\footnote{This is a footnote.}

\subsubsection{Subsubsection.}
This is a run-in heading in bold face.
Normal,
\textit{Italics,}
\textsl{Slanted,}
\textbf{Bold,}
\textsc{Small-Caps,}
\textit{\textbf{Italics Bold,}}
\textsl{\textbf{Slanted Bold,}}
\textsf{Sans Serif,}
\texttt{Monospaced.}

Avoid using \texttt{\textbackslash begin\{equation\}},
\texttt{\textbackslash begin\{gather\}},
\texttt{\textbackslash begin\{split\}},
and \texttt{\$\$}.
Always prefer \texttt{\textbackslash begin\{align\}}.
(One of) Euler's formula says
\begin{align*}
e^{i\pi}+1=0.
\end{align*}

\paragraph{Paragraph.}
This is an italicized run-in heading, and
\texttt{\textbackslash subparagraph} is \emph{explicitly} undefined.
Springer requires that table captions be above the table
and figure captions be below the figure,
as exemplified in Table~\ref{tab:table1} and \Figure~\ref{fig:figure1}.

\begin{table}[hp]
\centering
\capstart
\caption{Formats.}
\label{tab:table1}
\begin{tabular}{ll}
\toprule
\texttt{format=...} & \textbf{purpose} \\
\midrule
\texttt{eprint-draft} & full version, draft \\
\texttt{eprint} &
full version (\href{https://eprint.iacr.org/}{eprint.iacr.org}) \\
\texttt{focs-submission-draft} &
submission (FOCS), draft \\
\texttt{focs-submission} &
submission (FOCS) \\
\texttt{lncs-submission-draft} &
submission (IACR conferences), draft \\
\texttt{lncs-submission} &
submission (IACR conferences) \\
\texttt{lncs-camera-ready-draft} &
camera-ready, draft \\
\texttt{lncs-camera-ready-iacr} &
PDF archived by the IACR \\
\texttt{lncs-camera-ready-reference} &
PDF for Springer's reference \\
\texttt{lncs-camera-ready} &
source code to be processed by Springer \\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\capstart
\begin{tabular}{ll}
\toprule
\textbf{option} & \textbf{description} \\
\midrule
\texttt{layout=6x9} & use the 2022 layout \\
\texttt{layout=38x48} & use the 2023 layout \\
\texttt{layout=6.5x9} & use the FOCS submission layout \\
\texttt{opens-on=right} & make the main body start \\
& \qquad on an odd-numbered page \\
\texttt{opens-on=any} & do not make the main body start \\
& \qquad on an odd-numbered page \\
\texttt{bst=alpha} & use \texttt{alpha.bst} \\
\texttt{bst=splncs04} & use \texttt{splncs04.bst} \\
\texttt{links=colorful} & use colorful links \\
\texttt{links=blue} & use blue links \\
\texttt{fonts=computer-modern} & use Computer Modern fonts \\
\texttt{fonts=source} &
use \href{https://github.com/adobe-fonts}{Adobe Source} fonts \\
\texttt{fonts=times} & use Times fonts \\
\texttt{fonts=palatino} & use Palatino fonts \\
\texttt{fonts=libertine} & use Libertine fonts \\
\texttt{underlines=smart} & make underlines skip descenders \\
\texttt{underlines=dumb} & make underlines below descenders \\
\texttt{non-anonymous} & make the document non-anonymous \\
\texttt{no-page-limits} & mark the document \\
& \qquad as having no page limits \\
& \quad and do not mark appendix \\
& \qquad as ``supplementary materials'' \\
\texttt{no-table-of-contents} & do not show table of contents \\
\texttt{no-separate-title-page} & do not use a separate title page \\
\texttt{no-total-number-of-pages} & do not show the total number of pages \\
\texttt{no-lncs-array-table-margins} & do not use array/table inter-column \\
& \qquad margins from LNCS \\
\texttt{no-swapped-table-caption-margins} &
do not swap top/bottom margins \\
& \qquad for table captions \\
\bottomrule
\end{tabular}
\caption{Options for customizing the formats.
Not all options are effective for all formats, and
not all option combinations are possible.}
\label{fig:figure1}
\end{figure}

\section{Utilities}

The draft mode displays page borders,
which can be used to ensure that no content bleeds off the type center.

\subsection{Call-Out Boxes}

Use
\texttt{\textbackslash defcallout\textbackslash luoji\{Ji\}}
\emph{in the preamble}
to make
\luoji{This is a note from Ji.
\luoji{Nested call-outs are converted to paragraphs inside the same box.}}
control sequence \texttt{\textbackslash luoji} typeset a call-out box for Ji,
which is only shown in draft mode.
To make the control sequence
\texttt{\textbackslash long} (accept \texttt{\textbackslash par}),
use
\texttt{\textbackslash long%
\textbackslash defcallout\textbackslash luoji\{Ji\}}.
Using \texttt{\textbackslash long} is recommended.

\luoji{Note can go on empty paragraph,
but it looks weird and will disturb vertical typesetting.}

It is strongly discouraged to put a call-out box on an empty paragraph
as it makes vertical typesetting dependent on whether it is draft or not.
Note that even if there are no call-out boxes,
the typesetting result could be different for draft and non-draft
due to arithmetic errors
(in the draft version,
the type center is moved, and
rounding results could change).

\luoji{Note can start a paragraph.}
The colors of the boxes rotate so that it is easy to track which is where.

\subsection{Format- and Option-Dependent Control Sequences}

\subsubsection{Underlines.}
By default, ePrint uses descender-\underlined{skipping} underlines.
To \smartunderline{always} skip the descenders,
use \texttt{\textbackslash smartunderline}, and
to always \dumbunderline{stay} below the descenders,
use \texttt{\textbackslash dumbunderline}.

\subsubsection{Names of Referenced Objects.}
\texttt{\textbackslash Figure},
\texttt{\textbackslash Equation},
\texttt{\textbackslash Section},
\texttt{\textbackslash Figures},
\texttt{\textbackslash Equations}, and
\texttt{\textbackslash Sections}
provide the correct form of references:
\begin{itemize}
\item
In LNCS, they are Fig., Eq., Sect., Figs., Eqs., Sects., respectively.
This is required by Springer.
\item
In ePrint, they are Figure, Equation, Section, Figures, Equations, Sections.
\item
In the current format, they are
``\Figure'', ``\Equation'', ``\Section'',
``\Figures'', ``\Equations'', ``\Sections''.
\end{itemize}
Use
\texttt{\textbackslash WideNarrow},
\texttt{\textbackslash PageLimitsNoLimits},
\texttt{\textbackslash BibAlphaNumeric},
to choose one from the two candidates depending on the current style.
The type center is \WideNarrow{wide}{narrow},
there \PageLimitsNoLimits{is a}{are no} page limit\PageLimitsNoLimits{}{s},
and the bibliography is \BibAlphaNumeric{alphanumeric}{numeric}.
These control sequences are \texttt{\textbackslash long},
so they can accept multi-paragraph arguments.

\subsection{Mathematical Symbols}

All Greek letters
(including
\texttt{\textbackslash omicron} and \texttt{\textbackslash Omicron})
have their lowercase and uppercase control sequences,
and the uppercase letters are upright.
\begin{align*}
\Alpha,\alpha,{}&\vec{\Alpha},\vec{\alpha},&
\Beta,\beta,{}&\vec{\Beta},\vec{\beta},&
\Gamma,\gamma,{}&\vec{\Gamma},\vec{\gamma},&
\Delta,\delta,{}&\vec{\Delta},\vec{\delta},&
\Epsilon,\epsilon,{}&\vec{\Epsilon},\vec{\epsilon},&
\Zeta,\zeta,{}&\vec{\Zeta},\vec{\zeta},\\
\Eta,\eta,{}&\vec{\Eta},\vec{\eta},&
\Theta,\theta,{}&\vec{\Theta},\vec{\theta},&
\Iota,\iota,{}&\vec{\Iota},\vec{\iota},&
\Kappa,\kappa,{}&\vec{\Kappa},\vec{\kappa},&
\Lambda,\lambda,{}&\vec{\Lambda},\vec{\lambda},&
\Mu,\mu,{}&\vec{\Mu},\vec{\mu},
\displaybreak[3]\\
\Nu,\nu,{}&\vec{\Nu},\vec{\nu},&
\Xi,\xi,{}&\vec{\Xi},\vec{\xi},&
\Omicron,\omicron,{}&\vec{\Omicron},\vec{\omicron},&
\Pi,\pi,{}&\vec{\Pi},\vec{\pi},&
\Rho,\rho,{}&\vec{\Rho},\vec{\rho},&
\Sigma,\sigma,{}&\vec{\Sigma},\vec{\sigma},\\
\Tau,\tau,{}&\vec{\Tau},\vec{\tau},&
\Upsilon,\upsilon,{}&\vec{\Upsilon},\vec{\upsilon},&
\Phi,\phi,{}&\vec{\Phi},\vec{\phi},&
\Chi,\chi,{}&\vec{\Chi},\vec{\chi},&
\Psi,\psi,{}&\vec{\Psi},\vec{\psi},&
\Omega,\omega,{}&\vec{\Omega},\vec{\omega}.
\end{align*}
Control sequences similar to Office Equation Editor are provided:
\texttt{\textbackslash doubleA}
for blackboard bold,
\texttt{\textbackslash scriptA}
for usual handwritten,
\texttt{\textbackslash cursiveA}
for cursive handwritten,
\texttt{\textbackslash frakturA} and \texttt{\textbackslash fraktura}
for fraktur.
All these letter control sequences
can be used as superscripts and subscripts
without being wrapped inside braces, i.e.,
it is correct to write
\texttt{\$1\textasciicircum
\textbackslash cursiveA\textunderscore
\textbackslash lambda\$}
for $1^\cursiveA_\lambda$.
\begin{align*}
\doubleA,\scriptA,\cursiveA,{}&\frakturA,\fraktura,&
\doubleB,\scriptB,\cursiveB,{}&\frakturB,\frakturb,&
\doubleC,\scriptC,\cursiveC,{}&\frakturC,\frakturc,&
\doubleD,\scriptD,\cursiveD,{}&\frakturD,\frakturd,\\
\doubleE,\scriptE,\cursiveE,{}&\frakturE,\frakture,&
\doubleF,\scriptF,\cursiveF,{}&\frakturF,\frakturf,&
\doubleG,\scriptG,\cursiveG,{}&\frakturG,\frakturg,
\displaybreak[3]\\
\doubleH,\scriptH,\cursiveH,{}&\frakturH,\frakturh,&
\doubleI,\scriptI,\cursiveI,{}&\frakturI,\frakturi,&
\doubleJ,\scriptJ,\cursiveJ,{}&\frakturJ,\frakturj,&
\doubleK,\scriptK,\cursiveK,{}&\frakturK,\frakturk,\\
\doubleL,\scriptL,\cursiveL,{}&\frakturL,\frakturl,&
\doubleM,\scriptM,\cursiveM,{}&\frakturM,\frakturm,&
\doubleN,\scriptN,\cursiveN,{}&\frakturN,\frakturn,
\displaybreak[3]\\
\doubleO,\scriptO,\cursiveO,{}&\frakturO,\frakturo,&
\doubleP,\scriptP,\cursiveP,{}&\frakturP,\frakturp,&
\doubleQ,\scriptQ,\cursiveQ,{}&\frakturQ,\frakturq,\\ &&
\doubleR,\scriptR,\cursiveR,{}&\frakturR,\frakturr,&
\doubleS,\scriptS,\cursiveS,{}&\frakturS,\frakturs,&
\doubleT,\scriptT,\cursiveT,{}&\frakturT,\frakturt,
\displaybreak[3]\\
\doubleU,\scriptU,\cursiveU,{}&\frakturU,\frakturu,&
\doubleV,\scriptV,\cursiveV,{}&\frakturV,\frakturv,&
\doubleW,\scriptW,\cursiveW,{}&\frakturW,\frakturw,\\ &&
\doubleX,\scriptX,\cursiveX,{}&\frakturX,\frakturx,&
\doubleY,\scriptY,\cursiveY,{}&\frakturY,\fraktury,&
\doubleZ,\scriptZ,\cursiveZ,{}&\frakturZ,\frakturz.
\end{align*}
\texttt{\textbackslash 1} creates a blackboard bold $\1$,
which can be used as the indicator symbol.
\texttt{\textbackslash vec}
produces italicized boldfaced letters
(if the letters themselves are boldfaced
without \texttt{\textbackslash vec}, of course),
which is the orthodox.
The orthodox can be switched off using option \texttt{vec=bf}.
It works with Greek letters
(lowercase Greek letters are never upright except for omicron),
as shown above.
Below is a table of \texttt{\textbackslash vec}'s applied to Latin alphabet:
\begin{align*}
A,a,{}&\vec{A},\vec{a},&
B,b,{}&\vec{B},\vec{b},&
C,c,{}&\vec{C},\vec{c},&
D,d,{}&\vec{D},\vec{d},\\
E,e,{}&\vec{E},\vec{e},&
F,f,{}&\vec{F},\vec{f},&
G,g,{}&\vec{G},\vec{g},
\displaybreak[3]\\
H,h,{}&\vec{H},\vec{h},&
I,i,{}&\vec{I},\vec{i},&
J,j,{}&\vec{J},\vec{j},&
K,k,{}&\vec{K},\vec{k},\\
L,l,\ell,{}&\vec{L},\vec{l},\vec{\ell},&
M,m,{}&\vec{M},\vec{m},&
N,n,{}&\vec{N},\vec{n},
\displaybreak[3]\\
O,o,{}&\vec{O},\vec{o},&
P,p,{}&\vec{P},\vec{p},&
Q,q,{}&\vec{Q},\vec{q},\\ &&
R,r,{}&\vec{R},\vec{r},&
S,s,{}&\vec{S},\vec{s},&
T,t,{}&\vec{T},\vec{t},
\displaybreak[3]\\
U,u,{}&\vec{U},\vec{u},&
V,v,{}&\vec{V},\vec{v},&
W,w,{}&\vec{W},\vec{w},\\ &&
X,x,{}&\vec{X},\vec{x},&
Y,y,{}&\vec{Y},\vec{y},&
Z,z,{}&\vec{Z},\vec{z}.
\end{align*}
Several symbols are redefined to the sane versions:
\begin{align*}
\texttt{\textbackslash epsilon}&{}=\epsilon,&
\texttt{\textbackslash varepsilon}&{}=\varepsilon,&
\texttt{\textbackslash dumbepsilon}&{}=\dumbepsilon,\\
\texttt{\textbackslash phi}&{}=\phi,&
\texttt{\textbackslash varphi}&{}=\varphi,&
\texttt{\textbackslash dumbphi}&{}=\dumbphi,\\
\texttt{\textbackslash emptyset}&{}=\emptyset,&
\texttt{\textbackslash varnothing}&{}=\varnothing,&
\texttt{\textbackslash dumbemptyset}&{}=\dumbemptyset.
\end{align*}
It is wise to add more tests here ($v\nu\upsilon u\mu$):
\begin{align*}
&\sum_{i=1}^n{i}=\frac{n(n+1)}{2},
\WideNarrow{\qquad}{\quad}
\lim_{n\to\infty}{\int_{n^{-1}}^1{x\,\mathrm{d}x}}=\frac12,
\WideNarrow{\qquad}{\quad}
\bigcap_{n\geq 1}{\biggl\{
x
\,\bigg|\,
x\in\bigcup_{m\geq n}{A_m}
\biggr\}}
=\limsup_{n\to\infty}{A_n},\\
&
\Pr\left[\begin{aligned}
k&{}\draws\mathsf{Gen}(1^\lambda)\\
c&{}\draws\mathsf{Enc}(1^\lambda,k,m)
\end{aligned}
\::\:
\mathsf{Dec}(1^\lambda,k,c)=m
\right]
=1-\negl(\lambda)
\quad\forall m\in\bit^{\poly(\lambda)}.
\end{align*}

\subsection{Theorem Environments}

Use
\texttt{\textbackslash begin\{restated\}{\textbackslash ref\{label\}}}
to restate a theorem or typeset an unnumbered theorem.

\begin{restated}{Theorem~\ref{thm:theorem10}}
This is a restatement.
\end{restated}

\begin{restated}
{Theorem~\ref{thm:theorem10}}
[name]
This is a restatement with name.
\end{restated}

\noindent
Proofs and remarks are unnumbered.

\begin{proof}
This is \texttt{\textbackslash begin\{proof\}}.
\end{proof}

\begin{proof}
[\HyperTargetToThisLine{pf:lemma5}Lemma~\ref{lem:lemma5}]
This is
\begin{align*}
&\texttt{\textbackslash begin\{proof\}}\\%
&\texttt{[\textbackslash HyperTargetToThisLine\{pf:lemma5\}%
Lemma\textasciitilde\textbackslash ref\{lem:lemma5\}]}\\
&\texttt{...}\\
&\texttt{\textbackslash end\{proof\}}
\end{align*}
Use \texttt{\textbackslash qedhere} to place the tombstone symbol
on the last line of a displayed equation,
for which an alignment tab is required.
\begin{align*}
a+b&{}=c.
\qedhere
\end{align*}
\end{proof}

\begin{remarks}
This is \texttt{\textbackslash begin\{remarks\}}.
\end{remarks}

\begin{remarks}
[name]
This is \texttt{\textbackslash begin\{remarks\}[name]}.
\end{remarks}

\noindent
However, \texttt{\textbackslash begin\{remark\}} (singular form) is numbered.

\begin{remark}
This is \texttt{\textbackslash begin\{remark\}}.
\end{remark}

\begin{remark}
[name]
This is \texttt{\textbackslash begin\{remark\}[name]}.
\end{remark}

\noindent
No theorem environment uses a nested counter.

\begin{definition}
This is \texttt{\textbackslash begin\{definition\}}.
\end{definition}

\begin{definition}
[name]
This is \texttt{\textbackslash begin\{definition\}[name]}.
In LNCS formats, definitions are italicized,
making it tiring to read a security experiment.
Use
\texttt{\textbackslash begin\{itemize\}%
\textbackslash upshape%
\textbackslash item\textbackslash textbf\{Phase.\}}
to write them:
\begin{itemize}\upshape
\item\textbf{Setup.} Blah.
\item\textbf{Challenge.} Bruh.
\item\textbf{Guess.} Bleh.
\end{itemize}
\end{definition}

\begin{question}
This is \texttt{\textbackslash begin\{question\}}.
\end{question}

\begin{question}
[name]
This is \texttt{\textbackslash begin\{question\}[name]}.
\end{question}

\noindent
The style of definitions and questions depends on
whether the layout is LNCS or ePrint.

\begin{conjecture}
This is \texttt{\textbackslash begin\{conjecture\}}.
\end{conjecture}

\begin{conjecture}
[name]
This is \texttt{\textbackslash begin\{conjecture\}[name]}.
\end{conjecture}

\noindent
Corollaries, claims, lemmata, propositions, and theorems
share the same counter.

\begin{corollary}
This is \texttt{\textbackslash begin\{corollary\}}.
\end{corollary}

\begin{corollary}
[name]
This is \texttt{\textbackslash begin\{corollary\}[name]}.
\end{corollary}

\begin{claim}
This is \texttt{\textbackslash begin\{claim\}}.
\end{claim}

\begin{claim}
[name]
This is \texttt{\textbackslash begin\{claim\}[name]}.
\end{claim}

\begin{lemma}
[\hyperlink{pf:lemma5}{\P}]
\label{lem:lemma5}
This is \texttt{\textbackslash begin\{lemma\}%
[\textbackslash hyperlink\{pf:lemma5\}\{\textbackslash P\}]}.
It is a good idea to create two-way link between
a proposition and its proof.
\end{lemma}

\begin{lemma}
This is \texttt{\textbackslash begin\{lemma\}}.
\end{lemma}

\begin{proposition}
This is \texttt{\textbackslash begin\{proposition\}}.
\end{proposition}

\begin{proposition}
[name]
This is \texttt{\textbackslash begin\{proposition\}[name]}.
\end{proposition}

\begin{theorem}
This is \texttt{\textbackslash begin\{theorem\}}.
\end{theorem}

\begin{theorem}
[name]
\label{thm:theorem10}
This is \texttt{\textbackslash begin\{theorem\}[name]}.
\end{theorem}

\noindent
Assumptions and constructions, nothing special to be stated.

\begin{assumption}
This is \texttt{\textbackslash begin\{assumption\}}.
\end{assumption}

\begin{assumption}
[name]
This is \texttt{\textbackslash begin\{assumption\}[name]}.
\end{assumption}

\begin{construction}
This is \texttt{\textbackslash begin\{construction\}}.
\end{construction}

\begin{construction}
[name]
This is \texttt{\textbackslash begin\{construction\}[name]}.
\end{construction}

\subsection{Citations}

For citations of references, Springer LNCS prefers the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
such as~\cite{ref_article1,ref_lncs1,ref_book1}
and~\cite{ref_article1,ref_book1,ref_proc1,ref_url1},
if the numeric style is used.

The \texttt{cite} package is loaded and \texttt{nomove,noadjust} are set.
Using \texttt{noadjust} removes the extraneous space
in case of \texttt{\textbackslash begin\{lemma\}[\textbackslash cite{ref}]},
which is rendered as ``\texttt{Lemma 1 ([ABC])}''
instead of ``\texttt{Lemma 1 ( [ABC])}''.
Because of \texttt{noadjust},
no space is inserted for \texttt{word\textbackslash cite\{ref\}},
and it should be entered as
\texttt{word\textasciitilde\textbackslash cite\{ref\}}.
The \texttt{nomove} option does not manifest itself
for non-superscript citations.

Bugs of \texttt{\textbackslash doi}
in some versions of \texttt{splncs04.bst}
are mitigated.

Use
\href{https://github.com/cryptobib/export}{\texttt{cryptobib}}
to make citing cryptography literature easier.

\long\def\myrepeat#1\relax{#1\relax#1\relax}
\newcounter{mysectioncounter}

\myrepeat\myrepeat\myrepeat\myrepeat\myrepeat
\stepcounter{mysectioncounter}
\section{Additional Section \Roman{mysectioncounter}}
This is some content to make this section non-empty.
\relax

\let\myrepeat\relax
\let\mysection\relax

\subsection{Overlong Table of Contents is for Testing!}

Who says no?!
